Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-10 krs-survey.tex
Added subsections to 'Kn Acq and fusion' + filled part on Linked Data

>>>>

Let review shortly the three sub-categories of knowledge acquisition.

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf D.1 Acquisition and fusion}
            child {node {{\bf D.1.3} Linked Resources}}
            child {node {{\bf D.1.2} Interaction}}
            child {node {{\bf D.1.1} Sensing}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

\paragraph{Sensing}

\paragraph{Interaction}

\paragraph{Linked Knowledge Resources}

Robots, and in particular service robots, can access (with sometimes some
security-related constraints) the World Wide Web and remote knowledge stores.

The current shift towards the Semantic Web (\ie structured, annotated data that
are easily machine-processable) makes increasingly easy to have robots to reuse
autonomously this knowledge. The DBPedia project, for instance, illustrates
well the tendency: it provides an automatically generated RDF version of the
Wikipedia encyclopedia.

In its current state, the relevance of the DBPedia project in our context is
however limited: the triples that are extracted are mostly ``mechanical'' (like
the categories of a term, or factual informations extracted from Wikipedia's
InfoBox), and the vast majority of the knowledge actually contained in the
encyclopedia pages remains out of reach of automated parsers. Efforts like {\sc
ReVerb}~\cite{Fader2011} work however at automatic extraction of triples by
examining subject-verb-object relations in plain text.

Another notable project that seeks at providing large amount of
machine-friendly common-sense knowledge is the MIT's OpenMind
project~\cite{Singh2002}. The project is designed to let the general public
easily add common-sense statements in semi-controlled natural language, that is
then processed to a publicly available ontology.

An other approach that is easier at short-term to let robots remotely access
knowledge repositories consists is building robot-specific shared repositories,
with declarative and/or procedural (\ie, plan library) knowledge. The
RoboEarth~\cite{Waibel2011} project is an example of such an effort.
